Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-20 paper/uist_2016/paper.tex
findings

\section{Related Work}
\subsection{Digital Memories}
Rewind is guided by literature about mediated memories, which provides a theoretical underpinning behind how the Rewind experience is constructed. \textit{Mediated Memories in the Digital Age} offers inspiration informing the relationship between experiences and memories \cite{van2007mediated}. van Dijck notes, ``Remembering is vital to our well being, because without autobiographical memories we would have no sense of past or future, and we would lack any sense of continuity'' (pg. 3). Rewind aims to give the user this sense of continuity in a time segment which has a past and future. By picking a start and end location from a particular trip and generating a Rewind between these points, the user relives their memories in a continuous manner. Similarly in his famous seminal paper \textit{As we may think}, Vannevar Bush described \textit{memex}, the envisioned machinery to store infinite information and to allow free, collective access through``associative trails'', giving mankind the ability of``...forgetting the manifold things he does not need to have immediately at hand, with some assurance that he can find them again if they prove important''. Rewind in its most ambitious form, perhaps strives to become a potential counterpart of \textit{memex} for retrieving, and sharing of autobiographical memories of one’s sensory experiences about past visits.

@@

\section{The Rewind System}
\textit{Rewind} recreates the visual sensation of travelling down past routes using raw Google Location History data retrieved from location-tracking apps, including the default tracking behavior on Android phones. Differing from previously studied hyperlapse creation techniques by Kopft et al. and Joshi et al \cite{Kopf:2014:FHV:2601097.2601195, Joshi:2015:RHC:2809654.2766954}, \textit{Rewind} does not require any cinematic archives from the users, and it is computationally lightweight. \textit{Rewind} inputs geolocation data, maps out tracked trajectories, and outputs photo-video pairs with Google Street View images (although other street side photo services may be used). The sceneries in each photo-video pair are customized for each user based on times of the day, meteorological conditions and seasonal changes when the route was taken, providing users with multi-dimensional temporal cues. The current version of \textit{Rewind} is a web-based application implemented with Google Maps API and third-party JavaScript libraries, and therefore does not transfer sensitive user data nor store it. %\ref{fig:flowchart}

@@

\section{User Study}
\subsection{Research Questions}
% heather - is "digital memory" the right phrase for describing Rewind? Isn't rewind a medium for providing the cues to retrieve exisiting memories rather than creating new memories?
The Rewind system enables us to ask questions about people's attitudes and behaviors surrounding digital memories that were not possible to answer before due to the scarcity of comprehensive data about where a person has been. To understand what makes a digital memory meaningful to a person, we performed a within-subjects comparison of Rewinds and static photos. By comparing Rewinds to today's most prevalent form of digital memory media, we can distill what features make a Rewind meaningful and representative as a memory of a trip.

@@

% heather - I changed this part...
\begin{enumerate}
\item Memorability: How would \textit{Rewind} facilitate with the retrival of episodic memory? What types of users are most likely to recall their memories using \textit{Rewind}?
\item Believability:  How accurate are \textit{Rewind} artifacts in the eyes of the users' ? 
\item Desirability: What factors are inherent to users' decisions in preserving artifacts created by \textit{Rewind}?
\end{enumerate}

% heather - where to put this part or do we need a summary like this at all?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Our user study explored the following five metrics that could potentially influence the aforesaid three measurements of \textit{Rewind} vidoes. These five metrics are:
\item GPS usage: how self-identified regular GPS users and non-regular GPS users differ in their responses to \textit{Rewind} vidoes.
\item Traveller type: how self-identified frequent travellers and non-frequent travellers report to the three measurements of \textit{Rewind} vidoes differently.
\item Companions: how travelling companionship and solitude affect users' viewpoints on \textit{Rewind} vidoes.
\item Distance: how travelling distances affect users' perceptions of \textit{Rewind} vidoes.
\item Visit frequency: how visit frequency of a particular place influence users' reporting on \textit{Rewind} vidoes.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% heather - need to be rephrased perhaps? Should we give a high level summary of all the relationships we've found? More analysis to be done for photo vs. videos, another table?
\section{Findings}
The findings of our user study center on the participants’ relationship to the Rewinds generated from their location data. We focus on the participants’ judgments of their Rewinds’ memorability, believability, and desirability in comparison to their judgments of the photos paired with paired with the Rewinds. We also discuss the participants' interactions with and reactions to their Rewinds. The results use data from the user studies conducted with 12 men and 6 women. Half of the participants identified themselves as frequent travelers. Additionally, half of the participants were regular GPS users, that is people who used GPS even in locations already familiar to them.

@@

		\label{my-label}

@@

			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}33.33\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}57.98\%}     & \multicolumn{1}{c|}{50.83\%}                              & \multicolumn{1}{c|}{47.46\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}100.00\%}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}55.00\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}100.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}72.22\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}43.66\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}51.56\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}10.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}72.34\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}35.80\%}     \\ \cline{3-17} 

@@

			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{48.28\%}                              & \multicolumn{1}{c|}{56.30\%}                             & \multicolumn{1}{c|}{53.33\%}                              & \multicolumn{1}{c|}{54.39\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}61.70\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}89.74\%}        & \multicolumn{1}{c|}{60.00\%}                          & \multicolumn{1}{c|}{25.00\%}                         & \multicolumn{1}{c|}{55.56\%}                         & \multicolumn{1}{c|}{59.15\%}                         & \multicolumn{1}{c|}{50.00\%}                         & \multicolumn{1}{c|}{60.00\%}                         & \multicolumn{1}{c|}{52.17\%}                              & \multicolumn{1}{c|}{56.25\%}                             \\ \cline{3-17} 

@@

			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{68.42\%}                              & \multicolumn{1}{c|}{80.60\%}                             & \multicolumn{1}{c|}{77.05\%}                              & \multicolumn{1}{c|}{80.00\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}81.69\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}25.00\%}        & \multicolumn{1}{c|}{80.00\%}                          & \multicolumn{1}{c|}{60.00\%}                         & \multicolumn{1}{c|}{69.23\%}                         & \multicolumn{1}{c|}{90.00\%}                         & \multicolumn{1}{c|}{75.00\%}                         & \multicolumn{1}{c|}{0.00\%}                          & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}70.59\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}88.89\%}     \\ \cline{3-17} 

@@

			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{l|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}69.23\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}84.27\%}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}85.71\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}64.86\%}     & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}84.09\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}71.79\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}100.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}84.91\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}79.59\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}33.33\%} & \multicolumn{1}{c|}{69.70\%}                              & \multicolumn{1}{c|}{81.03\%}                             \\ \cline{3-17} 

@@

			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{13.33\%}                              & \multicolumn{1}{c|}{9.24\%}                              & \multicolumn{1}{c|}{12.50\%}                              & \multicolumn{1}{c|}{6.78\%}                              & \multicolumn{1}{c|}{12.16\%}                                   & \multicolumn{1}{c|}{10.00\%}                                & \multicolumn{1}{c|}{20.00\%}                          & \multicolumn{1}{c|}{37.50\%}                         & \multicolumn{1}{c|}{5.56\%}                          & \multicolumn{1}{c|}{7.04\%}                          & \multicolumn{1}{c|}{13.43\%}                         & \multicolumn{1}{c|}{10.00\%}                         & \multicolumn{1}{c|}{14.89\%}                              & \multicolumn{1}{c|}{9.88\%}                              \\ \cline{3-17} 

@@

			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}25.86\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}9.24\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20.83\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}1.75\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}12.77\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}25.64\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}0.00\%}   & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}0.00\%}  & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}11.11\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}10.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}19.70\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}40.00\%} & \multicolumn{1}{c|}{10.87\%}                              & \multicolumn{1}{c|}{17.50\%}                             \\ \cline{3-17} 

@@

% heather - didn't do the stats for video location vs photo locations, not sure if it is necessary? - photo vs video stats?
\subsubsection{Rewinds versus Photos}
When participants were shown a street side photo from their location history, they were asked whether they recognized the location in the photo. In 50\% of cases, participants said they did. When they were shown the Rewind associated with that photo, nearly every case had recognizable locations---97\%. This result is expected since Rewinds contain more location information than static photos, so if participants do not recognize some depicted locations, they still have many other chances to pick out locations they remember. Rewind memorability as calculated by whether participants could identify the particular trip they were on from watching the Rewind was 54\%. However, there were cases where the participant would only remember the photo after seeing its accompanying Rewind, which provided a context. More than one participant exclaimed after watching a Rewind, ``I recognize the photo now!''

\subsubsection{GPS Usage}
% Our findings show that GPS usage significantly affect the rememberance of locations $\chi^2(1,179) = 8.734$, p < 0.01, but does not impose a siginificant effect on trip rememberance. (GPS users remember locations 33% of the time whereas non-GPS users remember locations 58% of the time)
Our findings show that participants who are not regular GPS users remember locations and trips more often than participants who are regular GPS users (Figure~\ref{fig:gpsmemory}). When asked whether they remember the location or trip being shown in a photo or Rewind, participants who do not use GPS regularly gave a positive answer 58\% of the time for location remembrance and 56\% of the time for trip remembrance. Regular GPS users remembered locations 33\% of the time and trips 48\% of the time. The data shows that participants who are regular GPS users did not remember the locations they visited or trips they took as often as participants who are not regular GPS users. Since regular GPS users are frequently directed step-by-step on how to navigate their environment, they may not pay as much attention to their surroundings. This diminished locational awareness could be the reason why regular GPS users had a lower remembrance rate for locations and trips. From these percentages, we also see that regular GPS users remember trips more often than they remember locations, while there is little difference between the two for participants who do not use GPS regularly.

\subsubsection{Frequent Travelers}
% has no siginifant effects on location no trip rememberance
Our findings show that trip remembrance is influenced by the presence of travel companions. As one might imagine, trips that were taken with other people were more memorable than trips taken alone. Participants were not able to remember the exact trip of 33\% of Rewinds taken when they were traveling alone, but they could remember the exact trip of 89\% of Rewinds that were taken with company.

\subsubsection{Travel Companions}
% trip accompanies have siginificant effects on both location and trip rememberance. 
% location rememberance: travel alone -  100%, not alone - 55%, $\chi^2(1,94) = 31.812$, p < 0.01
% trip rememberance: travel alone - 62%, not alone - 90%, $\chi^2(1,133) = 9.016$, p < 0.01
Our findings show that trip remembrance is influenced by the presence of travel companions. As one might imagine, trips that were taken with other people were more memorable than trips taken alone. Participants were able to remember the exact trip of 67\% of Rewinds taken when they were traveling alone, but they could remember the exact trip of 90\% of Rewinds that were taken with company, with $\chi^2(1,133) = 9.016$, p < 0.01.

>>>>

\section{Related Work}
% heather - trips vs locations -> (define) semantic memory vs episodic memory - check references, relate to some work done by SenseCam perhaps?
% cut down GPS usage
\subsection{Digital Memories}
Rewind is guided by literature about mediated memories, which provides a theoretical underpinning behind how the Rewind experience is constructed. \textit{Mediated Memories in the Digital Age} offers inspiration informing the relationship between experiences and memories \cite{van2007mediated}. van Dijck notes, ``Remembering is vital to our well being, because without autobiographical memories we would have no sense of past or future, and we would lack any sense of continuity'' (pg. 3). Rewind aims to give the user this sense of continuity in a time segment which has a past and future. By picking a start and end location from a particular trip and generating a Rewind between these points, the user relives their memories in a continuous manner. Similarly in his famous seminal paper \textit{As we may think}, Vannevar Bush described \textit{memex}, the envisioned machinery to store infinite information and to allow free, collective access through``associative trails'', giving mankind the ability of``...forgetting the manifold things he does not need to have immediately at hand, with some assurance that he can find them again if they prove important''. Rewind in its most ambitious form, perhaps strives to become a potential counterpart of \textit{memex} for retrieving, and sharing of autobiographical memories of one’s sensory experiences about past visits.

@@

\section{The Rewind System}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% heather - depth of processing, retrival cues, uniqueness of encoding - Rewind ----> retrival cues
% http://www.psych.utoronto.ca/Neuropsychologylab/PDF/Depth%20of%20processing,%20retrieval%20cues,%20and.pdf
% go into introduction?
% come back to this section if time allows.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textit{Rewind} recreates the visual sensation of travelling down past routes using raw Google Location History data retrieved from location-tracking apps, including the default tracking behavior on Android phones. Differing from previously studied hyperlapse creation techniques, such as the studies by Kopft et al. and Joshi et al \cite{Kopf:2014:FHV:2601097.2601195, Joshi:2015:RHC:2809654.2766954}, \textit{Rewind} does not require any cinematic archives from the users, and it is computationally lightweight. \textit{Rewind} inputs geolocation data, maps out tracked trajectories, and outputs photo-video pairs with Google Street View images (although other street side photo services may be used). The sceneries in each photo-video pair are customized for each user based on times of the day, meteorological conditions and seasonal changes when the route was taken, providing users with multi-dimensional temporal cues. The current version of \textit{Rewind} is a open-sourced, web-based application implemented with Google Maps API and third-party JavaScript libraries, and therefore does not transfer sensitive user data nor store them. \textit{Rewind} can be accessed at [anonymized: url to rewind].  %\ref{fig:flowchart}

@@

\section{User Study}
\subsection{Research Questions}
% heather - is "digital memory" the right phrase for describing Rewind? Isn't rewind a medium for providing the cues to retrieve exisiting memories rather than creating new memories?
% talk about both within-subject and between-subject comparisons 
% within-subject -> memorability -> efficacy of semantic memory retrival vs episodic memory retrival -> video is better for both sementic and episodic
% between-subject -> memorability -> what type of users benefit the most from episodic memory retrival using Rewind; what kind of trip is Rewind best at capturing - (least frequently visited trip? most frequently visited trip? trip that's far away from home?)
The Rewind system enables us to ask questions about people's attitudes and behaviors surrounding digital memories that were not possible to answer before due to the scarcity of comprehensive data about where a person has been. To understand what makes a digital memory meaningful to a person, we performed a within-subjects comparison of Rewinds and static photos. By comparing Rewinds to today's most prevalent form of digital memory media, we can distill what features make a Rewind meaningful and representative as a memory of a trip.

@@

% heather - I changed this part...
\begin{enumerate}
\item Memorability: How would \textit{Rewind} facilitate the retrival of semantic and episodic memory? What types of users are most likely to recall their memories using \textit{Rewind}?
\item Believability:  How accurate are \textit{Rewind} artifacts in the eyes of the users' ? 
\item Desirability: What factors are inherent to users' decisions in preserving artifacts created by \textit{Rewind}?
\end{enumerate}

% heather - where to put this part or do we need a summary like this at all?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Our user study explored the following five metrics that could potentially influence the aforesaid three measurements of \textit{Rewind} vidoes. These five metrics are:
\begin{enumerate}
\item GPS usage: how self-identified regular GPS users and non-regular GPS users differ in their responses to \textit{Rewind} videos.
\item Traveler type: how self-identified frequent and non-frequent travelers report to the three measurements of \textit{Rewind} videos differently.
\item Companions: how traveling companionship and solitude affect users' viewpoints on \textit{Rewind} videos.
\item Distance: how traveling distances influence users' perceptions of \textit{Rewind} videos.
\item Visit frequency: how visit frequency of a particular place influences users' reporting on \textit{Rewind} videos.
\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% heather - need to be rephrased perhaps? Should we give a high level summary of all the relationships we've found? More analysis to be done for photo vs. videos, another table?
% semantic vs episodic memory
\section{Findings}
upper-bound estimates of event-related memories. 
The findings of our user study center on the participants’ relationship to the Rewinds generated from their location data. We focus on the participants’ judgments of their Rewinds’ memorability, believability, and desirability in comparison to their judgments of the photos paired with the Rewinds. We also discuss the participants' interactions with and reactions to their Rewinds. The results use data from the user studies conducted with 12 men and 6 women. Half of the participants identified themselves as frequent travelers. Additionally, half of the participants were regular GPS users, that is people who used GPS even in locations already familiar to them.

\subsection{Within-subject study}
\subsubsection{Memorability}
Within-subject comparison in our study reveals that participants are significantly better at recalling semantic memory of a particular location with \textit{Rewind} videos than with static street-view images, $\chi^2(1, 356) = 96.987$, $p < 0.01$. When being presented with a street-side image retrieved based on their location data, participants were able to recognize places visited 50\% of the time; yet recognition rate of locations reached 97\% when participants started playing accompanied \textit{Rewind} video, with a significant increase of 47\%. It is perhaps not too surprising as cinematic media like \textit{Rewind} video would provide users with more contextual meanings and retrival cues for semantic processing, as more than one participant have expressed their contentment after wathing \textit{Rewind} videos by claiming ``I recognize the photo now!'' when their initial attempts with static images were fruitless.

It could possibly be inferred that participants are likely to benefit more from \textit{Rewind} videos than static street-view images at recalling episodic memory. Although participants were not explicitly asked about trip rememberance when presented with static images, location rememberance from static images may serve as an upper-bound estimation of how much an individual could recall about a particular trip. - tbc
\subsubsection{Belivability and Desirability}
Although not statistically significant,

\subsection{Between-subject study}

\begin{table*}[t]
	\centering
	\caption{My caption}
	\small
	\label{within-subject-table}
	\begin{tabular}{c|c|c|c|c|c|c|c|c|}
		\cline{2-9}
		& \multicolumn{4}{c|}{Memorability} & \multicolumn{2}{c|}{Belivability} & \multicolumn{2}{c|}{Desirability} \\ \cline{2-9} 
		& \begin{tabular}[c]{@{}c@{}}video\\  location\end{tabular} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}photo\\ location/trip\end{tabular}} & \begin{tabular}[c]{@{}c@{}}video\\ trip\end{tabular} & photo & video & photo & video \\ \hline
		\multicolumn{1}{|c|}{N} & 177 & \multicolumn{2}{c|}{179} & 177 & 86 & 128 & 179 & 177 \\ \hline
		\multicolumn{1}{|c|}{\%} & 96.61\% & \multicolumn{2}{c|}{49.72\%} & 53.67\% & 77.91\% & 79.69\% & 10.61\% & 14.69\% \\ \hline
		\multicolumn{1}{|c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 96.987$\\ p = 0.0001\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 0.41$\\ p = 0.2611\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 214) = 0.02$\\ p = 0.4434\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356 ) = 0.995$\\ p = 0.1593\end{tabular}} \\ \hline
	\end{tabular}
\end{table*}
% 2nd table %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

		\label{between-subject-table}

@@

			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}33.33\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}57.98\%}     & \multicolumn{1}{c|}{50.83\%}                              & \multicolumn{1}{c|}{47.46\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}100.00\%}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}55.00\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}100.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}72.22\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}43.66\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}51.56\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}10.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}72.34\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}35.80\%}     \\ \cline{3-17} 

@@

			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{48.28\%}                              & \multicolumn{1}{c|}{56.30\%}                             & \multicolumn{1}{c|}{53.33\%}                              & \multicolumn{1}{c|}{54.39\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}61.70\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}89.74\%}        & \multicolumn{1}{c|}{60.00\%}                          & \multicolumn{1}{c|}{25.00\%}                         & \multicolumn{1}{c|}{55.56\%}                         & \multicolumn{1}{c|}{59.15\%}                         & \multicolumn{1}{c|}{50.00\%}                         & \multicolumn{1}{c|}{60.00\%}                         & \multicolumn{1}{c|}{52.17\%}                              & \multicolumn{1}{c|}{56.25\%}                             \\ \cline{3-17} 

@@

			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{68.42\%}                              & \multicolumn{1}{c|}{80.60\%}                             & \multicolumn{1}{c|}{77.05\%}                              & \multicolumn{1}{c|}{80.00\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}81.69\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}25.00\%}        & \multicolumn{1}{c|}{80.00\%}                          & \multicolumn{1}{c|}{60.00\%}                         & \multicolumn{1}{c|}{69.23\%}                         & \multicolumn{1}{c|}{90.00\%}                         & \multicolumn{1}{c|}{75.00\%}                         & \multicolumn{1}{c|}{0.00\%}                          & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}70.59\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}88.89\%}     \\ \cline{3-17} 

@@

			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{l|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}69.23\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}84.27\%}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}85.71\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}64.86\%}     & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}84.09\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}71.79\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}100.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}84.91\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}79.59\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}33.33\%} & \multicolumn{1}{c|}{69.70\%}                              & \multicolumn{1}{c|}{81.03\%}                             \\ \cline{3-17} 

@@

			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{13.33\%}                              & \multicolumn{1}{c|}{9.24\%}                              & \multicolumn{1}{c|}{12.50\%}                              & \multicolumn{1}{c|}{6.78\%}                              & \multicolumn{1}{c|}{12.16\%}                                   & \multicolumn{1}{c|}{10.00\%}                                & \multicolumn{1}{c|}{20.00\%}                          & \multicolumn{1}{c|}{37.50\%}                         & \multicolumn{1}{c|}{5.56\%}                          & \multicolumn{1}{c|}{7.04\%}                          & \multicolumn{1}{c|}{13.43\%}                         & \multicolumn{1}{c|}{10.00\%}                         & \multicolumn{1}{c|}{14.89\%}                              & \multicolumn{1}{c|}{9.88\%}                              \\ \cline{3-17} 

@@

			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}25.86\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}9.24\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20.83\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}1.75\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}12.77\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}25.64\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}0.00\%}   & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}0.00\%}  & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}11.11\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}10.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}19.70\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}40.00\%} & \multicolumn{1}{c|}{10.87\%}                              & \multicolumn{1}{c|}{17.50\%}                             \\ \cline{3-17} 

@@

% heather - didn't do the stats for video location vs photo locations, not sure if it is necessary? - photo vs video stats?
% will add this part back in within-group comparison

% \subsubsection{Rewinds versus Photos}
% When participants were shown a street side photo from their location history, they were asked whether they recognized the location in the photo. In 50\% of cases, participants said they did. When they were shown the Rewind associated with that photo, nearly every case had recognizable locations---97\%. This result is expected since Rewinds contain more location information than static photos, so if participants do not recognize some depicted locations, they still have many other chances to pick out locations they remember. Rewind memorability as calculated by whether participants could identify the particular trip they were on from watching the Rewind was 54\%. However, there were cases where the participant would only remember the photo after seeing its accompanying Rewind, which provided a context. More than one participant exclaimed after watching a Rewind, ``I recognize the photo now!''

\subsubsection{GPS Usage}
% Our findings show that GPS usage significantly affect the rememberance of locations $\chi^2(1,179) = 8.734$, p < 0.01, but does not impose a siginificant effect on trip rememberance. (GPS users remember locations 33% of the time whereas non-GPS users remember locations 58% of the time)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% heather - come back to this if time allows
% because memories are simply not encoded so there's no way to retrieve it in the first place?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Our findings show that GPS usage significantly affect participants' remembrance of locations $\chi^2(1,179) = 8.734$, p = 0.0016 ($< 0.01$), but does not impose significant effects on trip remembrance $\chi^2(1,177) = 0.713$, p = 0.1992 ($> 0.05$).  When asked whether they remember the location in a static photo, non-regular GPS users gave a positive answer 58\% of the time whereas regular GPS users gave a positive answer 33\% of the time. Although the difference between non-regular and regular GPS users' trip remembrance is not statistically significance, the between-subject percentage values still lean towards the observation that it is perhaps easier for non-GPS users to recall episodic memories from external memory cues, given that the total trip remembrance rate for non-GPS users is 48\% and that of GPS users is 56\%. Since regular GPS users are frequently directed step-by-step on how to navigate through their environment, regular GPS users may not need to pay as much attention to their surroundings, leading to potentially diminished locational awareness which could be the reason why regular GPS users had a lower remembrance rate for their ambience, particularly locations. \\

\subsubsection{Frequent Travelers}
% has no siginifant effects on location no trip rememberance
% needing explaination perhaps?
Although location rememberance is slightly higher for frequent traveler (51\% for frequent and 48\% for non-frequent), and trip rememberance is slightly higher for non-frequent traveler (53\% for frequent and 54\% for non-frequent), our study has not found these variances statistically significant.

\subsubsection{Travel Companions}
% trip accompanies have siginificant effects on both location and trip rememberance. 
% location rememberance: travel alone -  100%, not alone - 55%, $\chi^2(1,94) = 31.812$, p < 0.01
% trip rememberance: travel alone - 62%, not alone - 90%, $\chi^2(1,133) = 9.016$, p < 0.01
Our study shows that both location and trip remembrances are influenced by the presence of travel companions, yet in a opposite way. For location rememberance, participants who believed that they traveled alone reported 100\% successful recalls of locations compare to 55\% rate reported by participants who believed that they traveled in groups, with $\chi^2(1,94) = 31.812$, $p < 0.00001$. On the other hand, trip details tend to be more easily remembered during accompanied visits. Participants who believed that they traveled alone were able to remember the exact trip 62\% of the time from watching a \textit{Rewind} video, yet those who believed that they traveled with companions could remember the exact trip 90\% of the time, with $\chi^2(1,133) = 9.016$, p = 0.0013 $(< 0.01)$.
